The brightness and spatial distributions of terrestrial radio sources

### 2013-01-31 articles/Article-RFI-distribution/article-rfi-distribution.tex
Textual

So far, these are the expected histograms for pure noise and pure RFI that propagates through free space. However, the measured distribution is a mixture of the two. A perfect RFI detector would classify the samples in two groups; one group of samples that are not affected by RFI, and therefore contain noise only, and one one group of samples that are contaminated, and are the sum of RFI and noise. Real RFI detectors can classify samples into these groups to some extent, but due to false positives and false negatives, the groups will get mixed nevertheless. Even more, we still need to take into account that the samples classified as RFI are also affected by noise. Although this effect is moderate, because `most' RFI samples are of much higher amplitude than what is added because of the noise, we are interested in the low-level RFI samples, and the relative effect of noise on those samples is large.

>>>>

So far, these are the expected histograms for pure noise and pure RFI that propagates through free space. However, the measured distribution is a mixture of the two. A perfect RFI detector would classify the samples in two groups; one group of samples that are not affected by RFI, and therefore contain noise only, and one group of samples that are contaminated, and are the sum of RFI and noise. Real RFI detectors can classify samples into these groups to some extent, but due to false positives and false negatives, the groups will get mixed nevertheless. Even more, we still need to take into account that the samples classified as RFI are also affected by noise. Although this effect is moderate, because `most' RFI samples are of much higher amplitude than what is added because of the noise, we are interested in the low-level RFI samples, and the relative effect of noise on those samples is large.
